A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2024-03-29 tidyindex.qmd
include R file and the output

```{r eval = FALSE, echo = TRUE}
gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight)) 
```

>>>>

```{r eval = FALSE, echo = TRUE}
gggi %>% 
  init(id = country) %>%
  add_paras(gggi_weights, by = "variable") %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight)) 
```
